### 2019-04-19 chapters/0-abstract.tex
linebreaks

T₂w, DWI (12 b values, 0--2000 s/mm²), and T₂ data sets of 62 patients with
histologically confirmed PCa were acquired at 3T using surface array
coils. The DWI data sets were post-processed using monoexponential and kurtosis
models, while T₂w was standardized to a common scale. Local statistics and 8
different radiomics/texture descriptors were utilized at different configurations to
extract a total of 7105 unique per-tumor features. Regularized logistic
regression with implicit feature selection and leave pair out cross validation
was used to discriminate tumors with 3+3 vs >3+3 GS.

>>>>

T₂w, DWI (12 b values, 0--2000 s/mm²), and T₂ data sets of 62 patients with
histologically confirmed PCa were acquired at 3T using surface array coils. The
DWI data sets were post-processed using monoexponential and kurtosis models,
while T₂w was standardized to a common scale. Local statistics and 8 different
radiomics/texture descriptors were utilized at different configurations to
extract a total of 7105 unique per-tumor features. Regularized logistic
regression with implicit feature selection and leave pair out cross validation
was used to discriminate tumors with 3+3 vs >3+3 GS\@.
